---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# markup

<!-- badges: start -->
<!-- badges: end -->

A package for two-stage GMM production function estimation in R.


## Overview

The goal of markup is to provide a reliable way of estimating production functions from firm-level data in order to provide the output elasticities needed for determining firm-level markups following the approach by [De Loecker and Warzynski](https://doi.org/10.1257/aer.102.6.2437).

The package implements the two-stage estimation approach proposed by [Ackerberg, Caves, and Frazer](https://doi.org/10.3982/ECTA13408) in the main function `acf()`, supporting both Cobb-Douglas and translog specifications.

Additionally, the function `dlw()` provides an alternative version of the ACF-approach used by [De Loecker and Warzynski](https://doi.org/10.1257/aer.102.6.2437). It is based on a slightly different instrumentation in the second-stage GMM estimation.


## Installation

You can install the development version of markup from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("davben/markup")
```

## Example

Given a panel of firm-level production data, the basic approach of markup requires running a first-stage regression to estimate expected output \hat{\phi_{it}} and the random error \varepsilon_{it}. This is usually done via a higher-order polynomial with interactions and possibly time (and industry) fixed effects:

```{r example-stage-one, eval=FALSE}
library(tidyverse)
library(markup)

stage_one <- lm(y ~ l + ll + lll + k + kk + kkk + m + mm + mmm + lk + lm + km + lkm + factor(year), data = df)

df <- df %>%
    mutate(phi = predict(stage_one),
           epsilon = resid(stage_one)) %>%
    group_by(firm_id) %>%
    mutate(phi_lag = lag(phi, order_by = year)) %>%
    ungroup()
```

Production function coefficients can then be estimated like this:
```{r example-stage-two, eval=FALSE}
## Cobb-Douglas:
acf(initial_values = c(b0 = 0, bl = 0.4, bk = 0.6), data = df, type = "cd")

## Translog
acf(initial_values = c(b0 = 0, bl = 0.5, bk = 0.6, bll = -0.1, bkk = -0.05, blk = 0.1)), data = df, type = "tl")

```

Initial values for the GMM-estimation need to be provided.
These can either be chosen by estimating an OLS regression of the assumed production function and using its coefficients as a starting point.
Alternatively, the estimation can be run over a grid of initial values in order to test the robustness of the results.
